Kepler's Demographic Cliff: Ages of Young Stars and Planets in the Kepler Field

### 2024-05-17 paper/ms.tex
update ms

Cluster memberships are a delicate subject.
Figure~\ref{fig:agescalecompone} is showing putative ages for
a set of putative cluster members.  For NGC6811 and NGC6819, we
adopted candidate members from
\citet{2018A&A...618A..93C,CantatGaudin_2020} and
\citet{Kounkel_2020}. 
For Melange-3 we used the candidate members reported by
\citet{2022AJ....164...88B} and required ``offset'' tangential
velocities below 2\kms.  For Cep-Her we
used candidate members from Table~2 of \citet{Bouma_2022b}, requiring
``weights'' exceeding 0.1.
These lists almost certainly include non-members, in fractions that we
do not aim to quantify.  Even with these contaminants, we can compare
the relative age distributions derived by the different studies.

@@

\begin{figure*}[!t]
	\begin{center}
		\subfloat{
			\includegraphics[width=0.98\textwidth]{merged_lit_ages_vs_cluster_ages.pdf}
		}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    {\bf Literature age scale comparison.}
    Each point denotes the reported age of a star observed by Kepler,
    normalized by the age of a stellar ensemble in which the star
    is a candidate member.
    Rows show the available stellar ensembles, and columns show the
    various age-measurement techniques described in
    Appendix~\ref{app:litagecomparison}.
    Stars are sorted according to their median reported ages, and
    clusters are sorted by descending richness.
    Note that the horizontal axis is logarithmic; the first dotted line
    to the right of unity corresponds to a reported age ten times older
    than the cluster age.
	}
	\label{fig:agescalecompone}
\end{figure*}

>>>>

Cluster memberships are a delicate subject.
Figure~\ref{fig:agescalecompone} is showing putative ages for
a set of spatially and kinematically selected candidate cluster members.  For NGC6811 and NGC6819, we
adopted candidate members from
\citet{2018A&A...618A..93C,CantatGaudin_2020} and
\citet{Kounkel_2020}. 
For Melange-3 we used the candidate members reported by
\citet{2022AJ....164...88B} and required ``offset'' tangential
velocities below 2\kms.  For Cep-Her we
used candidate members from Table~2 of \citet{Bouma_2022b}, requiring
``weights'' exceeding 0.1.
These lists almost certainly include non-members, in fractions that we
do not aim to quantify.  Even with these contaminants, we can compare
the relative age distributions derived by the different studies.

@@

\begin{figure*}[!t]
	\begin{center}
		\subfloat{
			\includegraphics[width=0.98\textwidth]{merged_lit_ages_vs_cluster_ages.pdf}
		}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    {\bf Literature age scale comparison.}
    Each point denotes the reported age of a star observed by Kepler,
    normalized by the age of a stellar ensemble in which the star
    is a candidate member.
    We used memberships from spatio-kinematic estimates in the
    literature.
    Rows show the available stellar ensembles, and columns show the
    various age-measurement techniques described in
    Appendix~\ref{app:litagecomparison}.
    Stars are sorted according to their median reported ages, and
    clusters are sorted by descending richness.
    Note that the horizontal axis is logarithmic; the first dotted line
    to the right of unity corresponds to a reported age ten times older
    than the cluster age.
	}
	\label{fig:agescalecompone}
\end{figure*}
